---
title: "77 Districts Data Interactive Visualization of Nepal"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---
```{r setup, include=FALSE}
library(datasets)
library(flexdashboard)
library(yaml)
library(knitr)
library(DT)
library(rpivotTable)
library(ggplot2)
library(dplyr)
library(plotly)
library(openintro)
library(highcharter)
library(ggvis)
library(sp)
library(datasets)
```
```{r,echo=FALSE}
setwd("C:/Users/user/Desktop/publication/HDImap/NPL")
data <- read.csv("C:/Users/user/Desktop/publication/HDImap/NPL/districtsss.csv")
```
```{r}
mycolors=c("blue","#ffc125","darkgreen","darkorange")
```

Interactive Data Visualization
================================

Row
--------------------------------------------

### HDI, Literacy and Poverty of Nepal

```{r}
valueBox(length(data$id),
         icon ="fa-user" )

```

### AVERAGE HDI 

```{r}
 gauge(round(mean(data$HDI), 
 digits=2), 
 min= 0, 
 max=350,
 gaugeSectors(success= c(0,150),
 warning=c(150,240),
 danger=c(240,350),
 colors=c('green','yellow','red' )))
```

### AVERAGE Literacy 

```{r}
 gauge(round(mean(data$Lit), 
 digits=2), 
 min= 0, 
 max=350,
 gaugeSectors(success= c(0,150),
 warning=c(150,240),
 danger=c(240,350),
 colors=c('green','yellow','red' )))
```

### AVERAGE Poverty

```{r}
 gauge(round(mean(data$Pov), 
 digits=2), 
 min= 0, 
 max=350,
 gaugeSectors(success= c(0,150),
 warning=c(150,240),
 danger=c(240,350),
 colors=c('green','yellow','red' )))
```


### Province 1 

```{r}
valueBox(sum(data$Province=="Province 1"),
         icon='fa-building')

```

### Province 2 

```{r}
valueBox(sum(data$Province  == "Province 2"),
         icon='fa-building')

```

### Province 3 

```{r}
valueBox(sum(data$Province  == "Province 3"),
         icon='fa-building')

```

### Province 5 

```{r}
valueBox(sum(data$Province  == "Province 5"),
         icon='fa-building')

```

### Gandaki Pradesh

```{r}
valueBox(sum(data$Province  == "Gandaki"),
         icon='fa-building')

```

### Karnali Pradesh

```{r}
valueBox(sum(data$Province  == "Karnali"),
         icon='fa-building')

```

### Sudurpashchim Pradesh

```{r}
valueBox(sum(data$Province  == "Sudurpashchim"),
         icon='fa-building')

```

Row
-----------------------------------------------------------------------

### Interactive Province/Districts Bar Plot

```{r}
p1= data %>%
group_by(Province) %>%
summarise(count= n()) %>%
plot_ly(x= ~ Province,
          y= ~ count,
          color="blue",
          type='bar') %>%
layout(xaxis=list(title="Province By District"), 
yaxis=list(title='Count'))
p1

```

### Pie Chart Area by District of Nepal

```{r}
p2=data %>%
group_by(Province) %>%
summarise(count=n()) %>%
  filter(count >5) %>%
  plot_ly(labels= ~Province,
          values= ~count,
          marker= list(color=mycolors)) %>%
  add_pie(hole=0.2)  %>%
  layout(xaxis=list(zeroline=F,
                    showline=F,
                    showticklabels=F,
                    showgrid=F),
        yaxis=list(zeroline=F,
                 showline=F,
                 showticklabels=F,
                 showgrid=F))
p2
```

### Bar Plot of HDI VS Literacy of Nepal 

```{r}
p3=plot_ly(data,
x= ~HDI,
y= ~Lit,
text= paste("HDI:",data$HDI,
"Literacy Rate",
data$HDI),
type="bar") %>%
layout(xaxis= list(title="Human Development Index"),
yaxis=list(title="HDI VS Literacy"))
p3
```

Row
------------------------------------------------
### Scatter Plot Poverty VS Literacy

```{r}
p4=plot_ly(data, x=~Pov) %>%
add_markers(y= ~Lit,
text= ~paste("Literacy", Lit),
showlegend =F) %>%
add_lines(y= ~fitted(loess(Pov ~ Lit)),
name="Loess Smotother", 
color=I("#FFC125"),
showlegend= T,
line=list(width=5)) %>%
layout(xaxis=list(title="Poverty Index"),
yaxis=list(title="Literacy"))
p4
```

### Box Plot HDI and Literacy by Province

```{r}
data  %>%
group_by(Province) %>%
ggvis(~Province,~Lit,fill=~Province) %>%
layer_boxplots()
```

MAP 1
=======================================================================

Row
-----------------------------------------------------------------------

### VDC MAP OF NEPAL

```{r, echo=FALSE,fig.width = 40, fig.height = 7}
library(dplyr)
library(rgdal)
library(ggplot2)
library(sp)
library(rgeos) 
library(maptools)
setwd("C:/Users/user/Desktop/publication/HDImap/NPL")
nepal.adm3.shp<-readOGR(dsn='C:/Users/user/Desktop/publication/HDImap/NPL/npl_admbnda_adm2_nd_20190430.SHP', layer="npl_admbnda_adm2_nd_20190430", stringsAsFactors = FALSE)
nepal.adm3.shp.df<-fortify(nepal.adm3.shp, region = "ADM2_EN")
map <- ggplot(data = nepal.adm3.shp.df, aes(x =long, y = lat, group = group))
map + geom_path()
```


### DISRICT MAP OF NEPAL

```{r, echo=FALSE,fig.width = 10, fig.height = 7}
nepal.adm3.shp<-readOGR(dsn='C:/Users/user/Desktop/publication/HDImap/NPL/npl_admbnda_adm2_nd_20190430.SHP', layer="npl_admbnda_adm2_nd_20190430", stringsAsFactors = FALSE)
nepal.adm3.shp.df<-fortify(nepal.adm3.shp, region = "DIST_EN")
hpi.data <- read.csv("C:/Users/user/Desktop/publication/HDImap/NPL/districtsss.csv")
colnames(hpi.data) <- c("id","name","HDI","Lit","Pov")
nepal.adm3.shp.df<-merge(nepal.adm3.shp.df,hpi.data, by ="id")
map <- ggplot(data = nepal.adm3.shp.df, aes(x =long, y = lat, group = group))
map + geom_path()
```

Row
-----------------------------------------------------------------------

### CHLOROPLATH MAP OF NEPAL

```{r, echo=FALSE,fig.width = 22, fig.height = 7}
plot(map + 
  geom_polygon(aes(fill = HDI), color = 'gray', size = 0.1) +
  scale_fill_gradient(low = "#132B43", high = "#56B1F7", guide = "colourbar") +
  coord_fixed(1.3) +
  guides(fill=guide_colorbar(title="HDI Index")) + 
  theme(legend.justification=c(0,0), legend.position=c(0,0)))
theme_bare <- theme(
  axis.line = element_blank(), 
  axis.text.x = element_blank(), 
  axis.text.y = element_blank(),
  axis.ticks = element_blank(), 
  axis.title.x = element_blank(), 
  axis.title.y = element_blank(),
  legend.text=element_text(size=7),
  legend.title=element_text(size=8),
  panel.background = element_blank(),
  panel.border = element_rect(colour = "gray", fill=NA, size=0.5)  )
```

### COLOR CHLOROPLATH MAP OF NEPAL

```{r, echo=FALSE,fig.width = 10, fig.height = 7}
plot(map + 
  geom_polygon(aes(fill = HDI), color = 'gray', size = 0.1) +
  guides(fill=guide_colorbar(title="HDI Index")) + 
  scale_fill_gradient(high = "#e34a33", low = "#fee8c8", guide = "colorbar") +
  coord_fixed(1.3) +
  theme(legend.justification=c(0,0), legend.position=c(0,0)) +
  theme_bare)
```

MAP 2
=======================================================================

Row
-----------------------------------------------------------------------

### DISTRICT NAME MAP OF NEPAL

```{r, echo=FALSE,fig.width = 10, fig.height = 7}
centroids <- setNames(do.call(rbind.data.frame, by(nepal.adm3.shp.df, nepal.adm3.shp.df$group, function(x) {Polygon(x[c('long', 'lat')])@labpt})), c('long', 'lat')) 
centroids$label <-nepal.adm3.shp.df$id[match(rownames(centroids), nepal.adm3.shp.df$group) ]
centroids$label=hpi.data$name
plot(map + 
  geom_polygon(aes(fill = HDI), color = 'gray', size = 0.1) +
  guides(fill=guide_colorbar(title="HDI Index")) + 
  scale_fill_gradient(high = "#e34a33", low = "#fee8c8", guide = "colourbar") +
  coord_fixed(1.3) +
  theme(legend.justification=c(0,0), legend.position=c(0,0)) +
  with(centroids, annotate(geom="text", x = long, y = lat, label=label, size=2.5)) +
  theme_bare)
```

### HDI COLOR MAP OF NEPAL 

```{r, echo=FALSE,fig.width = 10, fig.height = 7}
centroids.selected <- centroids[centroids$label %in% (hpi.data[hpi.data$HDI>0.4,]$id),]
plot(map + 
  geom_polygon(aes(fill = HDI), color = 'gray', size = 0.1) +
  guides(fill=guide_colorbar(title="HDI Index")) + 
  scale_fill_gradient(high = "#e34a33", low = "#fee8c8", guide = "colorbar") +
  coord_fixed(1.3) +
  theme(legend.justification=c(0,0), legend.position=c(0,0)) +
  with(centroids.selected, annotate(geom="text", x = long, y = lat, label=label, size=2)) +
  theme_bare)
```

Row
-----------------------------------------------------------------------

### LITERSACY MAP OF NEPAL

```{r, echo=FALSE,fig.width = 10, fig.height = 7}
plot(map + 
  geom_polygon(aes(fill = Lit), color = 'gray', size = 0.1) +
  ggtitle("Literacy Index of Nepal") +
  guides(fill=guide_colorbar(title="Literacy Rate")) + 
  scale_fill_gradient(high = "#e34a33", low = "#fee8c8", guide = "colorbar") +
  coord_fixed(1.3) +
  theme(legend.justification=c(0,-0.1), legend.position=c(0.05,0)) +
  with(centroids.selected, annotate(geom="text", x = long, y = lat, label=label, size=2)) +
  theme_bare)
```

### POVERTY MAP OF NEPAL

```{r, echo=FALSE,fig.width = 10, fig.height = 7}
plot(map + 
  geom_polygon(aes(fill = Pov), color = 'gray', size = 0.1) +
  guides(fill=guide_colorbar(title="Poverty Index")) + 
  scale_fill_gradient(high = "#e34a33", low = "#fee8c8", guide = "colourbar") +
  coord_fixed(1.3) +
  theme(legend.justification=c(0,0), legend.position=c(0,0)) +
  with(centroids, annotate(geom="text", x = long, y = lat, label=label, size=2.5)) +
  theme_bare)
```

Data Table
===========

```{r, echo=FALSE}
setwd("C:/Users/user/Desktop/publication/HDImap/NPL")
data <- read.csv("C:/Users/user/Desktop/publication/HDImap/NPL/districtsss.csv")
datatable(data,
caption="failure Data",
rownames=T,
filter="top",
options=list(pageLength=25))
```

Pivottable
===========

```{r, echo=FALSE}
rpivotTable(data,
aggregatorName="Count",
cols="HDI",
rows="Province",
rendererName="Heatmap")
```


### HDI MAX

```{r, echo=FALSE}
valueBox(max(data$HDI),icon="fa-user")
```

### Average Literacy

```{r}
valueBox(round(mean(data$Lit),
digits=2),
icon="fa-area-user")
```

### Average HDI

```{r, echo=FALSE}
valueBox(round(mean(data$HDI),
digits=2),
icon="fa-area-user")
```

Report
=======
* This is a report on `r length(data$HDI)` HDI of Nepal failure.
* The average Literacy  was `r mean(data$Lit)`
* The average Area sq Km2 is`r mean(data$Area)`
This report was generated on `r format(Sys.Date(),format="%B %d%Y")`.

About Author
============
**Yagyanath Rimal**
20 th July, 1975
Pokhara Lekhnath Municipality Wardno 30 Kaski Nepal,
Postbox: 427
+977- 9846283010(Hand-phone) +977 061504116 (H)
 +977-561698(O)
E-mail: rimal.yagya@gmail.com
rimal.yagya@pu.edu.np

**Education** 
Master of Science in Information Technology (M.Sc. IT); Sikkim Manipal University of Health, Medical & Technological Sciences, India; with (First honors) 68.8 Percentage 2006.
**Publication (Books)**
1. Programming in C (Book 2013, Book Ozone publication Nepal)
2. Object Oriented Programming in C++ (Book, 2012 Asmita Publication Nepal)
3. A Reference Book on C Programming (Book, 2016 Ozone Publication Nepal) 
•4. A Reference Book on ICT for Nepalese Civil Servants (2019, Pairabi Publication, Kathmandu Nepal )

**Research**
*Instructional Material Management in Early- Childhood Development Center of Community Schools: A Case Study of Lekhnath Municipality, Kaski. UGC TU NEPAL (completed).
*Computer Literacy Among Faculty Members of Pokhara University:  A comparative study among constituent and affiliated campus (Research on going) UGC PURC Grant, Pokhara ( PURC ongoing)
Student’s Grade Analysis using Machine Learning Techniques of BE Student of Pokhara University Fall 2018 (Research on going Faculty Grant SOE, Pokhara University (PURC Pokhara University ongoing).

**Published Articles**
*Cognitive Aspects of Child Learning in Early Child Learning Centers
SILVER JUBLIEE SMARIKA Nepal  -2017   Shree Ghilibarang Primary School, Modi-1 Parbat   Nepal (Published)    
*Role of Physical Instructional Materials in Early Childhood Learning Centers
PRAGYAMANCH    Year: 30 Vol.: 15, September 2017      ISSN: 2392-442X (Published) 
*Does the Database Functional Dependency and its Normalization Make Uniform Database Management in Future?  International Research Journal of Mathematics, Engineering and IT ISSN: (2349-0322) Impact Factor- 5.489, Volume 5, Issue 6, June 2018(Published)
https://www.mbsresearch.com/files/journals/2018/June/_current_2018_Jul_kkl84kiEDwjlwZJ.pdf
https://www.aarf.asia/download.php?filename=../current/2018/Jul/KJg1YjjFGj1V1rn.pdf&new=PAPER2IRJMEITJUNE2018.pdf
*Machine Learning Random Forest Cluster Analysis for Large Overfitting Data: using R Programming (Proceedings of the 11th INDIACom; INDIACom-2017; IEEE Conference ID: 40353 2017 4th International Conference on “Computing for Sustainable Global Development”, 01st - 03rd March, 2017 Bharati Vidyapeeth's Institute of Computer Applications and Management (BVICAM), New Delhi (INDIA) Published)
https://drive.google.com/file/d/1CMafWFwkWypr_YUdvQqCT6k4ayqKPJdg/view?usp=sharing
*A BEST WAY OF MULTI-LEVEL IMBALANCE RESEARCH DATA HANDLING USING R PROGRAMMING ( © 2019 JETIR May 2019, Volume 6, Issue 5 www.jetir.org (ISSN-2349-5162 
http://www.jetir.org/papers/JETIRBW06018.pdf
*Deterministic Machine Learning Cluster Analysis of Research Data: using R Programming. International Journal of Machine Learning and Networked Collaborative Engineering, 3(01). Retrieved from 
https://www.mlnce.net/index.php/Home/article/view/73/51
*Machine Learning Prediction of Wikipedia Time Series Data using: R Programming. International Journal of Machine Learning and Networked Collaborative Engineering, 3(02). Retrieved from https://pdfs.semanticscholar.org/8d3d/9c5fb1d47ec31613382d30444a1c7280c24e.pdf?_ga=2.172258912.219399991.1570258590-1067851224.1570258590
https://www.mlnce.net/index.php/Home/article/view/82/54
*Neural Network Machine Learning Techniques for Large Noisy Data Prediction using R Programming ( © 2019 JETIR May 2019, Volume 6, Issue 5 www.jetir.org (ISSN-2349-5162 
http://www.jetir.org/papers/JETIRBW06019.pdf
*Correlation Coefficient Analysis of Data using R Programming: Does It Effectives? ( © 2019 JETIR May 2019, Volume 6, Issue 5 www.jetir.org (ISSN-2349-5162) 
http://www.jetir.org/papers/JETIRBW06020.pdf
*Multi-layer Neural Network Perception for Large Data Prediction using R Programming (CENTRAL ASIAN JOURNAL OF MATHEMATICAL THEORY AND COMPUTER SCIENCES http://centralasianstudies.org/index.php/CAJMTCS  Volume: 01 Issue: 01 | Aug 2019
http://centralasianstudies.org/index.php/CAJMTCS/article/view/2
*Cross-Validation Method for Overfitting Research Data Using R Programming
(CENTRAL ASIAN JOURNAL OF MATHEMATICAL THEORY AND COMPUTER SCIENCES http://centralasianstudies.org/index.php/CAJMTCS  Volume: 01 Issue: 01 | Aug 2019
http://centralasianstudies.org/index.php/CAJMTCS/article/view/3/6
*Basic Types of Regression Analysis in Various Research Data
(CENTRAL ASIAN JOURNAL OF MATHEMATICAL THEORY AND COMPUTER SCIENCES http://centralasianstudies.org/index.php/CAJMTCS  Volume: 01 Issue: 01 | Aug 2019
http://centralasianstudies.org/index.php/CAJMTCS/article/view/1
*Machine Learning Cluster Analysis for Large Categorical Data Using R Programming  (Recent Trends in Programming languages Vol 6, No 2 (2019)
*Regression Analysis of Research Data using R Programming (Recent Trends in Programming languages Vol 6, No 2 (2019)
*Machine Learning Prediction of Time Series Data: Decomposition and Forecasting methods (Springer Book Series, Learning and Analytics in Intelligent Systems: LAIS)
*Keras: The Best Machine Learning Process for Image Recognition and Classification (Springer Book Series, Learning and Analytics in Intelligent Systems: LAIS)
*Regression Analysis of Large Research Data: Dimensional Reduction Techniques (Springer Book Series, Learning and Analytics in Intelligent Systems: LAIS)
*Neural Network Machine Learning Analysis for Noisy Data: R Programming
International Journal of Engineering and Advanced Technology (IJEAT)ISSN: 2249 –8958, Volume-8 Issue-6, August 2019 
https://www.ijeat.org/wp-content/uploads/papers/v8i6/F8475088619.pdf

**Editorial /Reviewer Memberships**
*https://iiarp.org/committee.php
*http://ygrc19.com/index.php/international-advisory-board/
*http://www.gorea.org/
*https://conferencecommunity.org/committees.php
*https://www.firmsindia.org/editorialBoard.php
*http://www.ic3online.in/comm.html
*http://besh-conference.ga/Cambodia-17nov/committee.html

**Conference Paper Presentation**
*k-Nearest Neighbors Machine Learning Prediction of Cancer Categorical Data Using R Programming (international conference on Health Engineering in Disaster ICHED 2019 1-3 May 2019 Faculty of Science and technology Sphere and Pokhara University)
*Naïve Bayes Machine Learning Classification with R Programming: A case study of binary data sets (International conference on current status of cross discipline research in statistical science Department of Statists Tribhuvan University Prithiv Narayan Campus Nepal May 8-9 2019)

**Accepted Papers for Publications**
1.Self-organizing Map for Reducing High-dimensional Data Reduction
2.R Programming is Best Way for Social Media Network Analysis
3.Missing Data Handling using R programming a case study of Iris Data sets

**Professional Experience** 
Post: Lecturer 
Employer: Pokhara University, Kaski, Nepal 
(27/12/2009 to present) http://www.pu.edu.np 
Duties and responsibilities were: 
Teaching programming (C, C++) languages for BE Civil, BE Electrical, B. Pharmacy, BPH, undergraduate students. 
Hardware maintenance and Network Management 
Website uploads and designs its components 
Prepare manuals are available at: http://www.yagyarimal.com.np  

**Post: IT Faculty** 
Employer: College of Information Technology and Engineering, Kathmandu, Nepal (2/08/2006 to26/12/2009) http://www.cit.edu.np 
Duties and responsibilities were:  
Teaching programming languages in different semesters of undergraduate students (BCA, BIT and BE). 

**Computer Skills** 
Office Package (Basic of Information Technology, Word, Excel, Html, Access) 
Programming (Java, C, C++, Oracle, Visual Basic, Visual C++, C#, SPSS, R Programming) 
Electronic (Mathematic, Electronics/Network, Broadband Communication, Software Engineering, 
Advance Internet Programming (Asp, Xml, Perl, Scripting Languages Java/VB) 
Others (Client Server, Data Warehouse, E-Commerce, Digital Imaging, Wireless Mobile, E-CRM, Supply Chain Management, Secured E- Commerce, IT Law, Electives) etc.

@Book{,
  title = {R Markdown: The Definitive Guide},
  author = {Yihui Xie and J.J. Allaire and Garrett Grolemund},
  publisher = {Chapman and Hall/CRC},
  address = {Boca Raton, Florida},
  year = {2018},
  note = {ISBN 9781138359338},
  url = {https://bookdown.org/yihui/rmarkdown},
}

**Looking to get PhD in data sciences machine learning or AI**
